### 2023-11-24 main.tex
^^

\section{Introduction} 

@@

\mathbb{E}_{\mu^{rev}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt

@@

In this subsection we specialize the results of Section \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space

@@

\end{equation} and its generator reads

@@

where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the site generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a}^{x})_{a\in \{1,\ldots,N\}}$ respectively. 

@@

By Theorem \ref{thm-duality}, the process is dual to $(\bm{\xi}(t))_{t\geq0} $ defined on the enlarged configuration space where two extra-sites with unbounded maximal occupancy $\{0\}$ and $\{L+1\}$ have been added attached to the left of $\{1\}$ and to the right of $\{L+1\}$.
%\begin{equation}\label{stateSpaceDUAL-Chain}	
%	\widetilde{\Omega}=N_{0}^{N}\times\bigotimes_{x=1}^{L} \Omega_{x}\times N_{0}^{N}
Thus, the dual generator reads

@@

The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu$ the non-equilibrium stationary state measure of the the process $(\bm{n}(t))_{t\geq 0}$. For every $m\in\{1,\ldots,L\}$ we consider  $x_{k}\in\{1,\ldots,L\}$ and $a_{k}\in \{1,\ldots,N-1\}$ for every $k\in \{1,\ldots,m\}$ and we introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ meaning that 

@@

The duality function \eqref{dualityElements} computed in this dual configurations is 

@@

where $C(\nu,m)$ is a constant that depends on the number of correlated particles $m$ and on the maximal occupancy $\nu$. 
Therefore, up to this constant, $\mathbb{E}\left[D(\bm{n},\bm{\xi})\right]$ gives the non-equilibrium steady state $m-$points correlations. The following equalities hold using duality relation \eqref{duality-expectation}:

@@

		\frac{\mathbb{E}\left[\prod_{k=1}^{m}n_{a_{k}}^{x_{k}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]

@@

are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 This expectation can be computed by \eqref{ExptationSS} once the absorption probabilities are known.  For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. However, these absorption probabilities for higher point correlations fulfil some difference equations that are not easy to solve.

@@

Here we state the duality result for the thermalized multi-species stirring process with boundary driving. In the following, the dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively. To recall it we denote this dual space by $\widetilde{\Omega}_{L}$.

@@

			\mathbb{E}\left[n_{a}^{x}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt

@@

	\mathbb{E}\left[n_{a}^{x}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt

@@

		\mathbb{E}\left[n_{a}^{x}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}

@@

First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives

@@

	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.

@@

	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

We consider the first addend in the curly bracket of the previous equation. We add and remove $\xi_{k}^{1}$ at the exponent of $\left(\frac{\alpha_{k}}{|\alpha|}\right)$ and then we multiplying everything by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$. As a result, we have

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{k}^{1}-\xi_{k}^{1}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\nonumber\\=&
	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
	\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\nonumber

@@

	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets.

@@

		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})

>>>>

\section{Introduction} 
Boundary-driven particle systems are paradigmatic models for non-equilibrium statistical mechanics. In a boundary-driven system, the model is put in contact with reservoirs at its "boundaries" imposing different particle densities, and a current is generated through the system. In the long time limit, a non-equilibrium steady state sets in, with a stationary value of the current. The aim of this paper is to study the mathematical aspects of the stationary measure of boundary-driven {\em multispecies} particle systems \cite[....].

For the single species case, the exclusion process with open boundaries has been of crucial importance in our understanding of the structural properties of non-equilibrium state states, such as long-range correlations and non-local density large deviation functions. The results available for the exclusion process are rooted in the algebraic properties of the corresponding integrable quantum spin chain, i.e. the XXX Heisenberg Hamiltonian with $\mathfrak{su}(2)$ spins of value 1/2.
In this paper, we investigate the multispecies analog of the exclusion process in the boundary-driven context, i.e. the stirring process with open boundaries. The bulk part of the model with $N$ species is associated with the integrable Hamiltonian having  $\mathfrak{gl}(N)$ symmetry.

Our strategy to solve for the non-equilibrium steady state is of a probabilistic nature and relies on the use of duality. This approach, starting from the pioneering approach of [Presutti] and [Spohn] has been substantially developed in recent years to study stochastic processes in the boundary-driven set-up. The boundary-driven process is mapped to
a dual process with absorbing extra sites and the problem of describing the stationary state
is reduced to the problem of computing the absorption probabilities of the dual particles. 
In general, this is a difficult task. However, there are cases in which these absorption
probabilities can be computed thanks to the integrability property of the system.
For a recent example see [Frassek,Giardinà].

The remainder of this paper is organized as follows. In Section \ref{} we define the open multispecies stirring
process and provide its Lie algebraic description. In Section \ref{} we prove duality (Theorem \ref{}) 
and we show that, even in the presence of multispecies, the problem of characterizing the non-equilibrium 
steady state can be reduced to the computation of the absorption probabilities. Duality is proved when the 
system has a general spatial structure described by a graph. In Section \ref{} we obtain a closed formula 
for the stationary correlations (Theorem \ref{}) for the case of a one-dimensional chain with at most one 
particle per site, which is driven to steady-state by two reservoirs acting at the left and right boundaries. 
Here the computation of the absorption probabilities relies on the previously formulated Matrix Product Ansatz,
which is in fact also simplified by the use of duality. Finally in Section \ref{} we discuss a few extensions 
and generalizations of the model, including instantaneous thermalization limits, ......
In closing this introduction we mention that we are currently working on the boundary-driven multispecies 
model with non-compact Lie-algebras, both integrable and non-integrable, which will be presented in a 
future paper.

Acknowledgments: GNFM, PRIN, FAR UNIMORE,...

@@

\mathbb{E}_{\mu_{\text{rev}}}\left[D(\bm{n},\bm{\xi})\right]=\prod_{a=1}^{N-1}\left(\rho_{a}\right)^{\sum_{x\in V}\xi_{a}^{x}+\sum_{x\in V}\xi_{a}^{u(x)}}\qquad \forall \bm{n}\in \Omega,\quad\forall \bm{\xi}\in \widetilde{\Omega}\dt

@@

In the rest of this section we consider a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but with two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$). All the processes considered, denoted by $\left(\bm{n}(t)\right)_{t\geq0}$ with the generator specified in each subsection, will be defined on the space

@@

 The dual process will always be denoted by $(\bm{\xi}(t))_{t\geq 0}$ with the generator specified case by case. The dual configuration space is the one defined in \eqref{dualStateSpace} and adapted to the chain of size $L$ and with two extra-site $\{0,L+1\}$ attached to $\{1,L\}$ respectively. To recall it we denote this dual space by $\widetilde{\Omega}_{L}$, i.e.
\begin{equation}\label{dualSpace-chain}
	\widetilde{\Omega_{L}}=\mathbb{N}_{0}^{N}\otimes \Omega_{L}\otimes \mathbb{N}_{0}^{N}\dt
 As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by types $N$ (the empty). This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. This is a generalization for the non-integrable chain of the Corollary \ref{Corolollary-ABS_Corr-abstract}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ has generator

@@

where $\mathcal{L}_{x,x+1}$ is the edge generator defined in \eqref{edgeGenerator} acting on the bond $(x,x+1)$ and $\mathcal{L}_{\text{left}}$ and $\mathcal{L}_{\text{right}}$ are the generators \eqref{siteGenerator} acting on sites $\{1\}$ and $\{L\}$ with parameters $(\alpha_{a})_{a\in \{1,\ldots,N\}}$ and $(\beta_{a})_{a\in \{1,\ldots,N\}}$ respectively. 

@@

The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, has generator

@@

The dual process has absorbing boundaries. This implies that the chain is eventually voided and the steady state correlations of the original process can be written via the absorption probabilities of the dual process.\\
We call $\mu_{\text{NESS}}$ the non-equilibrium stationary steady state of the the process $(\bm{n}(t))_{t\geq 0}$, we denote by $\mathbb{E}_{\mu_{\text{NESS}}}[\cdot]$ the expectation with respect to this measure and and we call $\bm{\mathcal{Y}} = (\mathcal{Y}^{1},\ldots,\mathcal{Y}^{L})$ the random vector with law $\mu_{\text{NESS}}$. For every $m\in\{1,\ldots,L\}$ we consider  $x_{1},\ldots,x_{m}\in\{1,\ldots,L\}$ and $a_{1},\ldots,a_{m}\in \{1,\ldots,N-1\}$. We introduce the dual configuration  $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 

@@

The duality function is \eqref{dualityElements}, adapted to the chain. Therefore, we have that

@@

where $C(\nu,m)$ is a constant that depends on $m$ and on the maximal occupancy $\nu$. 
Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state. The following equalities hold using ergodicity and duality:

@@

		\frac{\mathbb{E}_{\mu_{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\mathcal{Y}_{a_{k}}^{x_{k}}=n_{a_{k}}^{x_{k}}\}}\right]}{C(\nu,m)}&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\bm{\xi})\right]=\lim_{t\to\infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\bm{\xi}(t))\right]

@@

are the absorption probabilities for the non-integrable chain, i.e. the probabilities that $t_{a}$ particles of species $a$ are absorbed at $\{0\}$. Here we have denoted $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$.
 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix \ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. However, these absorption probabilities for higher point correlations fulfil some difference equations that are not easy to solve.

@@

Here we state the duality result for the thermalized multi-species stirring process with boundary driving.

@@

			\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]&=\nu\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{a}^{x})\right]\\&=\nu\sum_{t_{a}=0}^{1}\left(\rho_{a}^{L}\right)^{t_{s}}\left(\rho_{s}^{R}\right)^{1-t_{s}}\mathbb{P}_{\delta_{a}^{x}}\left(\xi_{\infty}=t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)\dt

@@

	\mathbb{E}_{\mu_{\text{NESS}}}\left[\mathbbm{1}_{\{\mathcal{Y}_{a}^{x}=n_{a}^{x}\}}\right]=\nu\frac{\alpha_{a}(L|\beta|-|\beta|x+1)+\beta_{a}(|\alpha|x+1-|\alpha|)}{|\alpha||\beta|L-|\alpha||\beta|+|\alpha|+|\beta|}\dt

@@

		\mathbb{E}\left[\mathbbm{1}_{\{Y_{x}=a\}}\right]=\frac{\alpha_{a}(L-x+1)+\beta_{a}x}{L+1}

@@

First, we act with $\mathcal{L}_{\text{left}}^{TH}$ on $D(\bm{n},\bm{\xi})$. By writing explicitly $\rho_{a}^{L}=\frac{\alpha_{a}}{|\alpha|}$, this action gives

@@

	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.

@@

	\left.\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)-D(\bm{n},\bm{\xi})\right\}

@@

We consider the first addend in the curly bracket of the previous equation. We add and remove $|\xi^{1}|-\xi_{N}^{1}=\xi_{1}^{1}+\ldots+\xi_{N-1}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying by $\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-r_{\ell}+r_{\ell}-\xi_{\ell}^{1}+\xi_{\ell}^{1}}$. Thus, we have

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\nonumber\\
	&\left\{\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}+|\xi^{1}|-\xi_{N}^{1}-|\xi^{1}|+\xi_{N}^{1}}\right)\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\left(\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\right\}\nonumber\\
	&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\right)\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\right)\nonumber\\=&
	\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&
	\left(\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{r_{\ell}-\xi_{\ell}^{1}}\right)\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-r_{1}-\ldots-r_{N-1}}\left(\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)\nonumber

@@

	\left(\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right)
where in the last equality we used the multinomial theorem. \\ We now consider the second addend in the curly brackets\textbf{FINISH TO CHECK}.

@@

		&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\right)\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\right)\\=&D(\bm{n},\bm{\xi})
